---
title: "Assignment 9 TV Shows on Streaming Platforms"
author: "Brianna Humphries"
date: "10/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Cleaning

```{r clean, echo=TRUE}
library(readr)
#Data set found at:
#https://www.kaggle.com/ruchi798/tv-shows-on-netflix-prime-video-hulu-and-disney
#Updated May 25, 2020
#5611 total shows in data set
tvdata <- read_csv("tv_shows.csv", col_types = cols(X1 = col_skip(), type = col_skip(),
    `Rotten Tomatoes` = col_character(), 
    Netflix = col_factor(levels = c("0", "1")), 
    Hulu = col_factor(levels = c("0", "1")), 
    `Prime Video` = col_factor(levels = c("0", "1")), 
    `Disney+` = col_factor(levels = c("0", "1")), 
    type = col_factor(levels = c("0", "1"))))

#rename variables in data set for easier use
names(tvdata)[5] <- "RottenTomatoes"
names(tvdata)[8] <- "PrimeVideo"
names(tvdata)[9] <- "Disney"

#change variables to factor
tvdata$Year <- as.factor(tvdata$Year)
tvdata$Age <- as.factor(tvdata$Age)

#rename Age level all to All, and Platform levels to Yes or No
library(plyr)
tvdata$Age <- revalue(tvdata$Age, c("all"="All"))
tvdata$Netflix <- revalue(tvdata$Netflix, c("0"="No", "1"="Yes"))
tvdata$Hulu <- revalue(tvdata$Hulu, c("0"="No", "1"="Yes"))
tvdata$PrimeVideo <- revalue(tvdata$PrimeVideo, c("0"="No", "1"="Yes"))
tvdata$Disney <- revalue(tvdata$Disney, c("0"="No", "1"="Yes"))

#Order Age groups from young to old
tvdata$Age <- ordered(tvdata$Age, levels = c("All", "7+", "13+", "16+", "18+"))

#Remove % symbol from Rotten Tomatoes variable and change to numeric
tvdata$RottenTomatoes <- gsub("%", "", tvdata$RottenTomatoes)
tvdata$RottenTomatoes <- as.numeric(tvdata$RottenTomatoes)

#Show first 6 rows of dataset
head(tvdata)
attach(tvdata)
```
### Column Descriptions

**Title**: Title of TV show  
**Year**: Year in which the TV show was released  (1901-2020)  
**Age**: Target Age Group (All, 7+, 13+, 16+, 18+)  
**IMDb**: IMDb rating (0-10)  
**RottenTomatoes**: Rotten Tomatoes percentage rating (0-100)  
**Netflix**: Whether the TV show is found on Netflix (Yes or No)  
**Hulu**: Whether the TV show is found on Hulu (Yes or No)  
**PrimeVideo**: Whether the TV show is found on Prime Video (Yes or No)  
**Disney**: Whether the TV show is found on Disney+ (Yes or No)  

### Summary of Data
```{r summary, echo=TRUE}
#Show summary of data
summary(tvdata)
```

## Variable Distributions
### Years
```{r years, echo=TRUE}
library(ggplot2)
library(plotly)
#Years
#There are no shows in years 1901-1903, 1905-1913, 1915-1930, 1933, 1935-1942, 1944, and 1946
#Shows every year from 1947-2020
#No missing values in data set
yearP <- plot_ly(tvdata, x = ~Year) %>%
  add_histogram() %>% 
  layout(title = "Number of TV Shows per Year",
        xaxis = list(title = "Year"),
        yaxis = list(title = "Number of TV Shows"))
yearP
```

### Age Group
```{r agegrp, echo=TRUE}
#Age
#2446 missing values in data set, so graph includes 3165 observations
ageNA <- tvdata[complete.cases(tvdata$Age),] #data set without missing age obs.
ageP <- plot_ly(ageNA, x = ~Age) %>%
  add_histogram() %>% 
  layout(title = "Number of TV Shows per Age Group",
        xaxis = list(title = "Age Group"),
        yaxis = list(title = "Number of TV Shows"))
ageP
```

### IMDb Rating
```{r imdb, echo=TRUE}
#IMDb rating
#1161 missing values in data, so graph includes 4450 observations
imdbNA <- tvdata[complete.cases(tvdata$IMDb),] #data set without missing IMDb
imdbP <- plot_ly(imdbNA, x = ~IMDb) %>%
  add_histogram() %>% 
  layout(title = "Number of TV Shows per IMDb Rating",
        xaxis = list(title = "IMDb Rating"),
        yaxis = list(title = "Number of TV Shows"))
imdbP

#591 tv shows with IMDb ratings less than 6 (13.3%)
sum(na.omit(IMDb) < 6)
#3859 tv shows with IMDb ratings greater than or equal to 6 (86.7%)
sum(na.omit(IMDb) >= 6)
```

### Rotten Tomatoes Percent Rating
```{r rot, echo=TRUE}
#Rotten Tomatoes
#4600 missing values, so graph includes 1011 observations
rotNA <- tvdata[complete.cases(tvdata$RottenTomatoes),] #data set without NA RottenTomatoes
rotP <- plot_ly(rotNA, x = ~RottenTomatoes) %>%
  add_histogram() %>% 
  layout(title = "Number of TV Shows per Rotten Tomatoes Percentage",
        xaxis = list(title = "Rotten Tomatoes Percentage"),
        yaxis = list(title = "Number of TV Shows"))
rotP

#182 tv shows with IMDb ratings less than 6 (18.0%)
sum(na.omit(RottenTomatoes) < 60)
#829 tv shows with IMDb ratings greater than or equal to 6 (82.0%)
sum(na.omit(RottenTomatoes) >= 60)
```

### Streaming Platforms
```{r plat, echo=TRUE}
#number of tv shows in each platform
#No missing data in each platform
platMat <- sapply(X = tvdata[6:9], FUN = table) #frequency table
platforms <- c("Netflix", "Hulu", "Prime Video", "Disney+") #names of platforms
count_no <- platMat[1:1, 1:4] #extracts frequencies of "No" values
count_yes <- platMat[2:2, 1:4] #extracts frequencies of "Yes" values
count_yesN <- count_yes[1] #total number of shows in Netflix - 1931
count_yesH <- count_yes[2] #total number of shows in Hulu - 1754
count_yesP <- count_yes[3] #total number of shows in Prime Video - 2144
count_yesD <- count_yes[4] #total number of shows in Disney - 180
platdata <- data.frame(platforms, count_yes, count_no) #reorganization of freq table
#Plot number of tv shows in each platform as a grouped bar chart
plat <- plot_ly(platdata, x = ~platforms, y = ~count_yes, type = 'bar', name = 'Yes') %>%
  add_trace(y = ~count_no, name = 'No') %>%
  layout(title = "Number of TV Shows in Each Streaming Platform",
                        yaxis = list(title = 'Number of TV Shows'), 
                        xaxis = list(title = 'Streaming Platform'),
                        barmode = 'group',
                        legend = list(title = list(text = "Is the show in the platform?")))
plat #plot plat
```

## Correlation between IMDb Rating and Rotten Tomatoes Percentage
```{r corr, echo=TRUE}
#data set without missing rating variables
ratingNA <- tvdata[complete.cases(tvdata$RottenTomatoes, tvdata$IMDb),] #1008 observations
#fit <- lm(IMDb ~ RottenTomatoes, data=ratingNA) #for regression line
fit <- ratingNA %>% lm(RottenTomatoes ~ IMDb,.) %>% fitted.values
#Scatter plot of IMDb vs RottenTomatoes
ratePlot <- plot_ly(ratingNA, x = ~IMDb, y = ~RottenTomatoes, type="scatter", mode = "markers", text = ~paste("TV Show: ", Title, '<br>Year:', Year)) %>%
  add_trace(x=~IMDb, y=fit, mode = "lines") %>%
  layout(title = "IMDb Rating vs. Rotten Tomatoes Percentage", 
         xaxis = list(title = "IMDb Rating"), 
         yaxis = list(title = "Rotten Tomatoes Percentage"),
         showlegend = FALSE)
ratePlot

#Correlation test between IMDb and Rotten Tomatoes Ratings
cor.test(RottenTomatoes, IMDb) 
#p-value is less than 0.05, so correlation is significant
#Correlation coefficient: 0.489
```

## Platforms of "High Rating" TV Shows
```{r topRot, echo=TRUE}
#Create subset with top Rotten Tomatoes ratings from 80-100% or IMDb ratings from 8-10
#uses data without missing values since we are counting by platform
topRatings <- tvdata[which(tvdata$RottenTomatoes >= 80 | tvdata$IMDb >= 8.0),] #658 shows

#create dataset that includes the counts of the number of shows in or not in each platform with high ratings
platmatTop <- sapply(X = topRatings[6:9], FUN = table)
count_noTop <- platmatTop[1:1, 1:4] 
count_yesTop <- platmatTop[2:2, 1:4]
platdataTop <- data.frame(platforms, count_yesTop, count_noTop)

#Plot of how many shows with high ratings are in or not in each platform
platTop <- plot_ly(platdataTop, x = ~platforms, y = ~count_yesTop, type = 'bar', name = 'Yes') %>%
  add_trace(y = ~count_noTop, name = 'No') %>%
  layout(title = "Number of TV Shows in Each Streaming Platform with High Ratings",
                        yaxis = list(title = 'Number of TV Shows'), 
                        xaxis = list(title = 'Streaming Platform'),
                        barmode = 'group',
                        legend = list(title = list(text = "Is the show in the platform?")))

#Since data relies on there being a value in either IMDB or RottenTomatoes, then we need new count values that counts the tv shows in each platform when they don't have missings in both IMDb and RottenTomatoes
#Create dataset that includes values if not missing in both ratings
library(dplyr)
ratingNDNA <- full_join(imdbNA, rotNA) #4453 obs
#count how many of each platform are in this dataset
platmatNRA <- sapply(X = ratingNDNA[6:9], FUN = table)
count_noNRA <- platmatNRA[1:1, 1:4] 
count_yesNRA <- platmatNRA[2:2, 1:4]
platNA <- data.frame(platforms, count_yesNRA, count_noNRA) #reorganization of freq table
#Plot number of tv shows in each platform as a grouped bar chart
#for data without missing values in either IMDb or Rotten Tomatoes
#Shows that Netflix has more shows than Prime with this dataset
platNRA <- plot_ly(platNA, x = ~platforms, y = ~count_yesNRA, type = 'bar', name = 'Yes') %>%
  add_trace(y = ~count_noNRA, name = 'No') %>%
  layout(title = "Number of TV Shows in Each Streaming Platform (w/o missing)",
                        yaxis = list(title = 'Number of TV Shows'), 
                        xaxis = list(title = 'Streaming Platform'),
                        barmode = 'group',
                        legend = list(title = list(text = "Is the show in the platform?")))
platNRA #plot platNRA

#Calculate percent of tv shows that have a high rating
platTopPercY <- (count_yesTop / count_yesNRA)*100
platTopPercN <- (count_noTop / count_noNRA)*100
#Combine into percents and counts into dataset platdatatop
platdataTop <- cbind(platdataTop, platTopPercY)
platdataTop <- cbind(platdataTop, platTopPercN)
platdataTop <- cbind(platdataTop, count_yesNRA)
platdataTop <- cbind(platdataTop, count_noNRA)

#Percentage is of how many higher rating shows are in/not in the platform over the total number of shows in/not in the platform
#Ex: 33.4% of shows in Netflix have a high rating
#Ex: 30.7% of shows not in Prime Video have a high rating
platTopPercP <- plot_ly(platdataTop, x = ~platforms, y = ~platTopPercY, type = 'bar', name = 'Yes') %>%
    add_trace(y = ~platTopPercN, name = 'No') %>%
    layout(title = "Percent of TV Shows in Each Streaming Platform with High Ratings",
                        yaxis = list(title = 'Percent of TV Shows'), 
                        xaxis = list(title = 'Streaming Platform'),
                        barmode = 'group',
                        legend = list(title = list(text = "Is the show in the platform?")))

platTop #plot top counts
platTopPercP #plot top percents
```

## Age Groups of Platforms
```{r agePlat, echo=TRUE}
library(purrr)
#Count how many shows in platforms when missing ages values are taken out
platMatAgeCount <- sapply(X = ageNA[6:9], FUN = table)
platforms <- c("Netflix", "Hulu", "Prime Video", "Disney+")
count_noA <- platMatAgeCount[1:1, 1:4]
count_yesA <- platMatAgeCount[2:2, 1:4]
count_yesAN <- count_yesA[1]
count_yesAH <- count_yesA[2]
count_yesAP <- count_yesA[3]
count_yesAD <- count_yesA[4]

#Create datasets for each platform with count levels
ageNetflix <- ageNA %>% modify_if(is.character, as.factor) %>% group_by(Netflix, Age) %>% tally() %>% filter(Netflix == "Yes") %>% na.omit() %>% ungroup() %>% select(-Netflix) %>% 
  mutate(NetflixPer = (n / count_yesAN)*100)
names(ageNetflix)[2] <- "Netflix" 

ageHulu <- ageNA %>% modify_if(is.character, as.factor) %>% group_by(Hulu, Age) %>% tally() %>% filter(Hulu == "Yes") %>% na.omit() %>% ungroup() %>% select(-Hulu) %>% 
  mutate(HuluPer = (n / count_yesAH)*100)
names(ageHulu)[2] <- "Hulu" 

agePrime <- ageNA %>% modify_if(is.character, as.factor) %>% group_by(PrimeVideo, Age) %>% tally() %>% filter(PrimeVideo == "Yes") %>% na.omit() %>% ungroup() %>% select(-PrimeVideo) %>% 
  mutate(PrimePer = (n / count_yesAP)*100)
names(agePrime)[2] <- "PrimeVideo" 

ageDisney <- ageNA %>% modify_if(is.character, as.factor) %>% group_by(Disney, Age) %>% tally() %>% filter(Disney == "Yes") %>% na.omit() %>% ungroup() %>% select(-Disney) %>% 
  mutate(DisneyPer = (n / count_yesAD)*100)
names(ageDisney)[2] <- "Disney" 

#Join datasets by Age and replace any null values to be 0
agePlatData <- full_join(ageNetflix, ageHulu, by="Age")
agePlatData <- full_join(agePlatData, agePrime, by="Age")
agePlatData <- full_join(agePlatData, ageDisney, by="Age")
agePlatData <- agePlatData %>% mutate_all(~replace(., is.na(.), 0))

#create distribution of platforms for shows without missing ages
ageplatNA <- plot_ly(platNA, x = ~platforms, y = ~count_yesA, type = 'bar', name = 'Yes') %>%
  add_trace(y = ~count_noA, name = 'No') %>%
  layout(title = "Number of TV Shows in Each Streaming Platform (w/o missing)",
                        yaxis = list(title = 'Number of TV Shows'), 
                        xaxis = list(title = 'Streaming Platform'),
                        barmode = 'group',
                        legend = list(title = list(text = "Is the show in the platform?")))
ageplatNA #plot

#Create plot of count of ages by platforms
agePlat <- plot_ly(agePlatData, x = ~Age, y = ~Netflix, type = 'bar', name = 'Netflix', marker = list(color = "firebrick")) %>%
    add_trace(y = ~Hulu, name = 'Hulu', marker = list(color = "#00EE76")) %>%
    add_trace(y = ~PrimeVideo, name = 'Prime Video', marker = list(color = "#000033")) %>%
    add_trace(y = ~Disney, name = 'Disney+', marker = list(color = "#0A47CC")) %>%
    layout(title = "Number of Shows of Each Rating in Each Platform",
                        yaxis = list(title = 'Number Of Shows'), 
                        xaxis = list(title = 'Age Group'),
                        barmode = 'group',
                        legend = list(title = list(text = "Platform")))

#Create plot of percent of ages by platforms
agePlatPer <- plot_ly(agePlatData, x = ~Age, y = ~NetflixPer, type = 'bar', name = 'Netflix', marker = list(color = "firebrick")) %>%
    add_trace(y = ~HuluPer, name = 'Hulu', marker = list(color = "#00EE76")) %>%
    add_trace(y = ~PrimePer, name = 'Prime Video', marker = list(color = "#000033")) %>%
    add_trace(y = ~DisneyPer, name = 'Disney+', marker = list(color = "#0A47CC")) %>%
    layout(title = "Percent of TV Shows in Each Age Group for Each Platform",
                        yaxis = list(title = 'Percent of TV Shows in Platform'), 
                        xaxis = list(title = 'Age Group'),
                        barmode = 'group',
                        legend = list(title = list(text = "Platform")))
agePlat
agePlatPer
```

## Platforms Content by Release Year
```{r platYear, echo=TRUE}
#create data sets with counts of tv shows per year for each platform
yearNetflix <- tvdata %>% modify_if(is.character, as.factor) %>% group_by(Netflix, Year) %>% tally() %>% filter(Netflix == "Yes") %>% na.omit() %>% ungroup() %>% select(-Netflix) %>% 
  mutate(NetflixPer = (n / count_yesN)*100)
names(yearNetflix)[2] <- "Netflix" 

yearHulu <- tvdata %>% modify_if(is.character, as.factor) %>% group_by(Hulu, Year) %>% tally() %>% filter(Hulu == "Yes") %>% na.omit() %>% ungroup() %>% select(-Hulu) %>% 
  mutate(HuluPer = (n / count_yesH)*100)
names(yearHulu)[2] <- "Hulu" 

yearPrime <- tvdata %>% modify_if(is.character, as.factor) %>% group_by(PrimeVideo, Year) %>% tally() %>% filter(PrimeVideo == "Yes") %>% na.omit() %>% ungroup() %>% select(-PrimeVideo) %>% 
  mutate(PrimePer = (n / count_yesP)*100)
names(yearPrime)[2] <- "PrimeVideo" 

yearDisney <- tvdata %>% modify_if(is.character, as.factor) %>% group_by(Disney, Year) %>% tally() %>% filter(Disney == "Yes") %>% na.omit() %>% ungroup() %>% select(-Disney) %>% 
  mutate(DisneyPer = (n / count_yesD)*100)
names(yearDisney)[2] <- "Disney" 

#join datasets and replace NAs with 0
yearPlatData <- full_join(yearNetflix, yearHulu, by="Year")
yearPlatData <- full_join(yearPlatData, yearPrime, by="Year")
yearPlatData <- full_join(yearPlatData, yearDisney, by="Year")
yearPlatData <- yearPlatData %>% mutate_all(~replace(., is.na(.), 0))
yearPlatData$Year <- as.factor(yearPlatData$Year)
yearPlatData <- yearPlatData[order(yearPlatData$Year),] #order Years

#plot of show count per year per platform
yearPlatPlot <- plot_ly(yearPlatData, x = ~Year, y = ~Netflix, type = 'scatter', mode = "lines", name = 'Netflix', line = list(color = "firebrick")) %>%
    add_trace(y = ~Hulu, name = 'Hulu', mode="lines", line = list(color = "#00EE76")) %>%
    add_trace(y = ~PrimeVideo, name = 'Prime Video', mode="lines", line = list(color = "#000033")) %>%
    add_trace(y = ~Disney, name = 'Disney+', mode="lines", line = list(color = "#0A47CC")) %>%
    layout(title = "Each Platform's Content Available by Release Year",
                        yaxis = list(title = 'Number of TV Shows'), 
                        xaxis = list(title = 'Year'),
                        legend = list(title = list(text = "Platform")))

yearPlatPlot

#plot of show percent per year per platform
yearPlatPlotPer <- plot_ly(yearPlatData, x = ~Year, y = ~NetflixPer, type = 'scatter', mode = "lines", name = 'Netflix', line = list(color = "firebrick")) %>%
    add_trace(y = ~HuluPer, name = 'Hulu', mode="lines", line = list(color = "#00EE76")) %>%
    add_trace(y = ~PrimePer, name = 'Prime Video', mode="lines", line = list(color = "#000033")) %>%
    add_trace(y = ~DisneyPer, name = 'Disney+', mode="lines", line = list(color = "#0A47CC")) %>%
    layout(title = "Each Platform's Content Available by Release Year",
                        yaxis = list(title = 'Percent of TV Shows in Platform'), 
                        xaxis = list(title = 'Year'),
                        legend = list(title = list(text = "Platform")))

yearPlatPlotPer

```

## Relation of Different Platforms
```{r alluv, echo=TRUE}
# create alluvial diagram
library(ggalluvial)
library(ggfittext)
Nalluv <- ggplot(tvdata, aes(axis1 = Netflix, axis2 = Hulu, axis3 = PrimeVideo, axis4 = Disney, y = stat(count))) + 
  geom_alluvium(aes(fill=Netflix), knot.pos=0) +
  geom_stratum(alpha=.5) + 
  geom_text(stat = "stratum", aes(label= after_stat(stratum))) + 
  scale_x_discrete(limits = c("Netflix", "Hulu", "Prime Video", "Disney"), expand = c(.1, .1)) +
  labs(title = "TV Shows of Streaming Platforms", subtitle = "stratified by Netflix", 
       y = "Frequency") + 
  theme_minimal()

Halluv <- ggplot(tvdata, aes(axis1 = Netflix, axis2 = Hulu, axis3 = PrimeVideo, axis4 = Disney, y = stat(count))) + 
  geom_alluvium(aes(fill=Hulu), knot.pos=0) +
  geom_stratum(alpha=.5) + 
  geom_text(stat = "stratum", aes(label= after_stat(stratum))) + 
  scale_x_discrete(limits = c("Netflix", "Hulu", "Prime Video", "Disney"), expand = c(.1, .1)) +
  labs(title = "TV Shows of Streaming Platforms", subtitle = "stratified by Hulu", 
       y = "Frequency") + 
  theme_minimal()

Palluv <- ggplot(tvdata, aes(axis1 = Netflix, axis2 = Hulu, axis3 = PrimeVideo, axis4 = Disney, y = stat(count))) + 
  geom_alluvium(aes(fill=PrimeVideo), knot.pos=0) +
  geom_stratum(alpha=.5) + 
  geom_text(stat = "stratum", aes(label= after_stat(stratum))) + 
  scale_x_discrete(limits = c("Netflix", "Hulu", "Prime Video", "Disney"), expand = c(.1, .1)) +
  labs(title = "TV Shows of Streaming Platforms", subtitle = "stratified by Prime Video", 
       y = "Frequency") + 
  theme_minimal()

Dalluv <- ggplot(tvdata, aes(axis1 = Netflix, axis2 = Hulu, axis3 = PrimeVideo, axis4 = Disney, y = stat(count))) + 
  geom_alluvium(aes(fill=Disney), knot.pos=0) +
  geom_stratum(alpha=.5) + 
  geom_text(stat = "stratum", aes(label= after_stat(stratum))) + 
  scale_x_discrete(limits = c("Netflix", "Hulu", "Prime Video", "Disney"), expand = c(.1, .1)) +
  labs(title = "TV Shows of Streaming Platforms", subtitle = "stratified by Disney+", 
       y = "Frequency") + 
  theme_minimal()

Nalluv
Halluv
Palluv
Dalluv
```

```{r freq3, echo=TRUE}
#There are no shows that are in all 4 platforms
plat4 <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "Yes"),]

#How many shows are on 3 platforms
#Not in Disney - 31
plat3NHP_D <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "No"),]
#Not in Hulu - 0
plat3N_HPD <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "Yes"),]
#Not in Netflix - 0
plat3_NHPD <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "Yes"),]
#Not in Prime - 1
plat3NH_PD <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "No" & tvdata$Disney == "Yes"),]
head(plat3NH_PD)
#Combine into 1 dataset - 32 (0.57% of data set)
plat3 <- rbind(plat3NHP_D, plat3NH_PD)

#How many shows are on 1 platforms
#Only in Netflix - 1748 - 90.5% of Netflix
plat1N <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "No" & tvdata$Disney == "No"),]
#Only in Hulu - 1452 - 82.8% of Hulu
plat1H <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "No" & tvdata$Disney == "No"),]
#Only in Prime - 1889 - 88.1% of Prime Video
plat1P <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "No"),]
#Only in Disney - 156 - 87.7& of Disney+
plat1D <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "No" & tvdata$Disney == "Yes"),]
#Combine into 1 dataset - 5245 obs (93.5% of data set)
plat1 <- rbind(plat1N, plat1H, plat1P, plat1D)

#How many shows are on 2 platforms
#In Netflix and Hulu - 87
plat2NH <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "No" & tvdata$Disney == "No"),]
#In Netflix and Prime - 59
plat2NP <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "No"),]
#In Netflix and Disney - 5
plat2ND <- tvdata[which(tvdata$Netflix == "Yes" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "No" & tvdata$Disney == "Yes"),]
#In Hulu and Prime - 165
plat2HP <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "No"),]
#In Hulu and Disney - 18
plat2HD <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "Yes" & tvdata$PrimeVideo == "No" & tvdata$Disney == "Yes"),]
#In Prime and Disney - 0
plat2PD <- tvdata[which(tvdata$Netflix == "No" & tvdata$Hulu == "No" & tvdata$PrimeVideo == "Yes" & tvdata$Disney == "Yes"),]
#Combine into 1 dataset - 334 obs (5.95% of data set)
plat2 <- rbind(plat2NH, plat2NP, plat2ND, plat2HP, plat2HD, plat2PD)
```
